\documentclass[12pt,a4paper]{article}
\usepackage{microtype}
\usepackage{hyperref}

\begin{document}

\title{Default disambiguation for online parsers\\Experiment}
\maketitle

This artefact provides scripts to reproduce the results from the evaluation
section of the paper. Reviewers may run the experiment using the same setup as
used in the paper using the VirtualBox image (Section \ref{quickstart}); run
the experiment on their own machine (Section \ref{fromscratch}); only run a
subset of the experiment (Section \ref{subset}); or only generate the tables
using pre-built results from the paper (Section \ref{tablesonly}).

\noindent Username and password for the virtual machine: \textbf{user} / \textbf{user}

\section{Running the experiment}

\subsection{Quickstart}
\label{quickstart}

Runtime: $\sim$3-4 hours

\noindent To run the experiment execute \texttt{./build\_paper.sh} (located in
\texttt{$\sim$/experiment/}). This will run all benchmarks and should take
approximately 3-4 hours on a machine with an i7 and PyPy installed (the use of
CPython and/or VirtualBox will likely increase this runtime). After the
benchmarks have finished running, the results will automatically be analysed,
and latex tables will be generated in \texttt{latex/}. The produced tables
correspond to the paper as follows:

\begin{itemize}
    \item Table 1: \texttt{tbl\_valid.tex}
    \item Table 2: \texttt{tbl\_breakdown.tex}
    \item Table 3: \texttt{tbl\_bench\_all.tex}
    \item Table 4: \texttt{tbl\_bench\_hist.tex}
    \item Table 5: \texttt{tbl\_bench\_stack.tex}
    \item Table 6: \texttt{tbl\_bench\_line.tex}
\end{itemize}

\subsection{Running without the VM}
\label{fromscratch}

Runtime: $\sim$3-4 hours

\noindent Reviewers may alternatively clone the experiment
repository from \url{https://github.com/softdevteam/auto_lbox_experiments} and
run it on their own machine. Note however, that the repository does not contain
the files necessary to run the experiment in the exact setup of the paper and
since the tests are randomised results may differ slightly from the paper.

\subsection{Running a subset}
\label{subset}

Runtime: $\sim$1 hour

\noindent Reviewers may run a subset of the benchmark suite with
\texttt{./build\_subset.sh}, which reduces the total runtime of the experiment.
Note that in this case the results will likely differ a lot from the paper.

\subsection{Produce tables using prebuilt data}
\label{tablesonly}

Runtime: $\sim$1-2 seconds

\noindent Reviewers who only want to reproduce the tables without running the
benchmarks themselves can run \texttt{./build\_tables.sh}. This will use the
benchmark results from the paper (which come packaged with this VM) to generate
the latex tables.

\section{Using the editor}

To see automatic language boxes in action, reviewers may run the editor Eco and
try out some of the compositions. Eco can be started either by using the link
on the desktop or executing \texttt{cd eco; ./bin/eco} in a terminal. Reviewers
may then open any of the examples in \texttt{$\sim$/eco\_examples} (which correspond
to Figures 1, 7, and 8 in the paper) and follow the instructions in the comments.

\end{document}
